\documentclass[10pt,journal,compsoc, twoside]{IEEEtran}

\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi

\usepackage[left=2cm, top=3cm, right=2cm, bottom=3cm]{geometry}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{amsmath}%
\usepackage{multirow}
\usepackage{xargs}
\usepackage{hyperref}
\usepackage{pgfplots}
\usepackage{listings}
\usepackage{longtable}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{colortbl}
\usepackage{array}
\usepackage{calc}
\usepackage{amssymb}
\usepackage[author={Mathieu}]{pdfcomment}
\usepackage{lipsum}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%


\begin{document}

\title{A New Taxonomy of Bugs Based on the Location of the Correction: An Empirical Study}

\author{

\IEEEauthorblockN{
  Mathieu	Nayrolles\IEEEauthorrefmark{1},
  Abdelwahab Hamou-Lhadj\IEEEauthorrefmark{1},
  Abdou	Maiga\IEEEauthorrefmark{1},
  Alf	Larsson\IEEEauthorrefmark{2},
  Sigrid Eldh\IEEEauthorrefmark{2}}

\IEEEauthorblockA{\vspace{0.2cm}\IEEEauthorrefmark{1}Software Behaviour Analysis (SBA) Research Lab
\\ECE, Concordia University, Montr\'eal, Canada
\\\{m\_nayrol, a\_maiga, abdelw\}@ece.concordia.ca
}
\IEEEauthorblockA{\\\vspace{0.2cm}\IEEEauthorrefmark{2}Ericsson
\\Stockholm, Sweden\\
\{alf.larsson, sigrid.eldh\}@ericsson.com}

}


% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Bug taxonomy, Bug tracking systems, Empirical studies,
Software maintenance
\end{IEEEkeywords}


\IEEEpeerreviewmaketitle


\input{introduction}
\input{preliminaries}
\input{study}
\input{discussion}
\input{relwork}


\section{Conclusion}

In this paper, we proposed a taxonomy of bugs and performed an empirical study on two large open source datasets: the Netbeans IDE and the Apache SoftwareFoundation’s projects. Our study aimed to analyse: (1) the proportion of each type of bugs; (2) the complexity of each type in terms of severity, reopening and duplication; and (3) the required time to fix a bug depending on its type.The key findings are:  Types 2 and 4 account for 65\% of the bugs.  Types 2 and 4 have a similar severity compared to Types 1 and 3.  Types 2 and 4 are more complex (reopening) and have a bigger impact (duplicate) than Types 1 and 3.  It takes more time to fix Types 2 and 4 than Types 1 and 3. Our taxonomy and results can be used to classify past and new researches in several active areas such as bug reproduction and triaging, bug prediction, and detection of duplicate bug reports. Moreover, if one could predict the type of a bug at submission time, we belive that most of these areas could be improved since we can use results of fixing old bugs when new and related bugs arrive. As future work, we plan to test our taxonomy on additional opensource systems such as Eclipse or Linux. In addition, we will experiment with proprietary systems at Ericsson and report the differences between open source and proprietary systems

\section{Reproduction Package}

We provide a repoduction package that is publicly available at https://research.mathieu-nayrolles.com/taxonomy/reproduction.zip.
All the instructions needed to reproduce our results are self contained in the provided archive.


% \input{appendice}


% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

\bibliographystyle{IEEEtran}
\bibliography{library}

\end{document}
